LSOA Deprevation maps

### 2021-08-10 LSOA Deprevation.Rmd
Adding the difference in IMD score map

# plotting the indices of dep 2019 of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `IMDScore`)) +
  scale_fill_continuous(name = "IMD Score", low = "green", high = "red") +
  labs(caption = "Winchester")
```
####Difference from 2010 to 2019

here

#####Looking at the cities in more detail

>>>>

# plotting the indices of dep 2019 of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `IMDScore`)) +
  scale_fill_continuous(name = "IMD Score", low = "green", high = "red") +
  labs(caption = "Winchester")
```
####Difference from 2015 to 2019
```{r Creating the dfference in IMD score variable}
imd_lsoa_2015 <- readr::read_csv(paste0(dataFolder, "Indices of Multiple Deprivation/Indices_of_Multiple_Deprivation_(IMD)_2015.csv"))
imd_lsoa_2019 <- readr::read_csv(paste0(dataFolder, "Indices of Multiple Deprivation/Indices_of_Multiple_Deprivation_(IMD)_2019.csv"))
imd_lsoa_2015$imd2015 <- imd_lsoa_2015$`Index of Multiple Deprivation (IMD) Score`
imd_lsoa_2015$imd2019 <- imd_lsoa_2019$`IMDScore`
merged_imd <- merge(imd_lsoa_2015, imd_lsoa_2019, by = "lsoa11cd", all = TRUE)
names(merged_imd)
merged_imd$imd_diff<-as.numeric(merged_imd$imd2019)-merged_imd$imd2015
summary(merged_imd)
```
```{r Mapping the change in IMD Score}
merged_imd$lsoa11cd <- merged_imd$"lsoa11cd" #creating a variable with the LSOA code in the same name as in sf_data
lsoa_imd20152019 <- merge(lsoa_sf_data, merged_imd) #merging these
names(lsoa_imd20152019)##BROKEN
##ggplot2::ggplot(lsoa_imd20152019) +
 ## geom_sf(aes(fill=mc_diff))+ 
  ##scale_fill_continuous(name="Change in Gas: Mean kWh per meter", low="green",high="red")+
  ##labs(caption ="Solent (all MSOAs)")
```
#####Looking at the cities in more detail
```{r Southampton LSOA Gas}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(merged_imd, LAD11NM == "Southampton")
# plotting the gas consumption of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `imd_diff`)) +
  scale_fill_continuous(name = "Change in IMD score", low = "green", high = "red") +
  labs(caption = "Southampton")
```
```{r Portsmouth LSOA Gas}
#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
mapData <- dplyr::filter(merged_imd, LAD11NM == "Portsmouth")
# plotting the gas consumption of Portsmouth in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `imd_diff`)) +
  scale_fill_continuous(name = "Change in IMD score", low = "green", high = "red") +
  labs(caption = "Portsmouth")
```
```{r Winchester LSOA Gas}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(merged_imd, LAD11NM == "Winchester")
# plotting the gas consumption of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `imd_diff`)) +
  scale_fill_continuous(name = "Change in IMD score", low = "green", high = "red") +
  labs(caption = "Winchester")
```
